Elephace: Elephant Re-identification Using Deep Learning

### 2022-05-05 Report/PaperForReview.tex
add tables
add authors

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}
\maketitle

@@

\begin{table}[]
\begin{tabular}{@{}lllllll@{}}
\toprule
                       & \multicolumn{3}{l}{ResNet50}               & \multicolumn{3}{l}{InceptionV3} \\ \midrule
\multicolumn{1}{l|}{n} & top-1 & top-3 & \multicolumn{1}{l|}{top-5} & top-1     & top-3    & top-5    \\
\multicolumn{1}{l|}{1} & 0.439 & 0.572 & \multicolumn{1}{l|}{0.703} & 0.449     & 0.585    & 0.659    \\
\multicolumn{1}{l|}{3} & 0.776 & 0.9   & \multicolumn{1}{l|}{0.943} & 0.810     & 0.923    & 0.959    \\
\multicolumn{1}{l|}{5} & 0.852 & 0.928 & \multicolumn{1}{l|}{0.955} & 0.918     & 0.966    & 0.976    \\
\multicolumn{1}{l|}{7} & 0.931 & 0.978 & \multicolumn{1}{l|}{0.989} & 0.991     & 0.995    & 0.995    \\
\multicolumn{1}{l|}{9} & 0.953 & 0.985 & \multicolumn{1}{l|}{0.992} & 0.998     & 0.998    & 0.993   
\end{tabular}
\caption{Accuracy results on Zoo elephants datasets using Few Shot for re-identification}
\label{tab:few-shot-results}
\end{table}

>>>>

\author{Deepak Duggirala\\
Indiana University\\
{\tt\small deduggi@iu.edu}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Gandhali Marunmale\\
Indiana University\\
{\tt\small gamarunm@iu.edu}
}
\maketitle

@@

\begin{table}[]
\begin{tabular}{@{}lllllll@{}}
\toprule
                       & \multicolumn{3}{l}{ResNet50}               & \multicolumn{3}{l}{InceptionV3} \\ \midrule
\multicolumn{1}{l|}{n} & top-1 & top-3 & \multicolumn{1}{l|}{top-5} & top-1     & top-3    & top-5    \\ \midrule
\multicolumn{1}{l|}{1} & 0.439 & 0.572 & \multicolumn{1}{l|}{0.703} & 0.449     & 0.585    & 0.659    \\
\multicolumn{1}{l|}{3} & 0.776 & 0.9   & \multicolumn{1}{l|}{0.943} & 0.810     & 0.923    & 0.959    \\
\multicolumn{1}{l|}{5} & 0.852 & 0.928 & \multicolumn{1}{l|}{0.955} & 0.918     & 0.966    & 0.976    \\
\multicolumn{1}{l|}{7} & 0.931 & 0.978 & \multicolumn{1}{l|}{0.989} & 0.991     & 0.995    & 0.995    \\
\multicolumn{1}{l|}{9} & 0.953 & 0.985 & \multicolumn{1}{l|}{0.992} & 0.998     & 0.998    & 0.993   
\end{tabular}
\caption{Accuracy results on Zoo elephants datasets using Few Shot for re-identification}
\label{tab:few-shot-results}
\end{table}

\begin{table}[]
\begin{tabular}{@{}lllllll@{}}
\toprule
                       & \multicolumn{3}{l}{ResNet50}               & \multicolumn{3}{l}{InceptionV3} \\ \midrule
\multicolumn{1}{l|}{n} & top-1 & top-3 & \multicolumn{1}{l|}{top-5} & top-1     & top-3    & top-5    \\ \midrule
\multicolumn{1}{l|}{1} & 0.047 & 0.086 & \multicolumn{1}{l|}{0.106} & 0.048     & 0.088    & 0.112    \\
\multicolumn{1}{l|}{3} & 0.111 & 0.179 & \multicolumn{1}{l|}{0.223} & 0.089     & 0.170    & 0.220    \\
\multicolumn{1}{l|}{5} & 0.165 & 0.264 & \multicolumn{1}{l|}{0.323} & 0.165     & 0.255    & 0.321    \\
\multicolumn{1}{l|}{7} & 0.212 & 0.342 & \multicolumn{1}{l|}{0.413} & 0.252     & 0.408    & 0.478    \\
\multicolumn{1}{l|}{9} & 0.303 & 0.446 & \multicolumn{1}{l|}{0.525} & 0.280     & 0.460    & 0.510   
\end{tabular}
\caption{Accuracy results on Wild elephants datasets using Few Shot for re-identification}
\label{tab:few-shot-results-wild}
\end{table}
